### 2017-07-19 README.Rmd

Two categorical variables (diff in proportions) (not yet implemented)

```
mtcars %>%
  specify(am ~ vs) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in prop")
```

>>>>

Two categorical variables (diff in proportions)

```
mtcars %>%
  specify(am ~ vs) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in props")
```
